Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-09-21 doc/manuscript/ESSDmanuscript.Rmd
remove NEE, total.ecosystem from variable mapping diagram & manuscript

\clearpage
```{r, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them.} In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes minimal non-respiratory C fluxes,... (Chapin et al. 2006); 2- assumes that change in foliage biomass is negligible (see note 7); 3- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 4- incomplete: excludes belowground components;  5-incomplete: excludes breakage into pieces less than dead wood threshold size; 6-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter, may exclude branch fall; 7- measurements often limited to decomposition of relatively fine litter and may exclude branches and stems below the dead wood size threshold and/or the more decomposed layers of the O horizon; 8 - foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year); 9 - excludes branch fall, which is necessary for a full accounting of woody productivity but is typically assumed negligible for calculations of net biomass change."}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/C_variable_mapping.png")
```

@@

Define relationship among NEE, NEP, and delta.C., especially noting role of harvest [@chapin_reconciling_2006].

>>>>

\clearpage
```{r, out.width = "15cm", echo = FALSE, fig.cap = "\\textbf{Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them.} In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes that change in foliage biomass is negligible (see note 7); 2- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 3- incomplete: excludes belowground components;  4-incomplete: excludes breakage into pieces less than dead wood threshold size; 5-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter, may exclude branch fall; 6- measurements often limited to decomposition of relatively fine litter and may exclude branches and stems below the dead wood size threshold and/or the more decomposed layers of the O horizon; 7 - foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year); 8 - excludes branch fall, which is necessary for a full accounting of woody productivity but is typically assumed negligible for calculations of net biomass change."}
#this is for a two-column figure. for one-column figure, use {r, out.width = "8.3cm", echo = FALSE, fig.cap = "one column figure"}
knitr::include_graphics("figures_tables/C_variable_mapping.png")
```

@@

### 2021-09-21 doc/manuscript/ESSDmanuscript.tex
remove NEE, total.ecosystem from variable mapping diagram & manuscript

\clearpage
\begin{figure}
\includegraphics[width=15cm]{figures_tables/C_variable_mapping} \caption{\textbf{Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them.} In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes minimal non-respiratory C fluxes,... (Chapin et al. 2006); 2- assumes that change in foliage biomass is negligible (see note 7); 3- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 4- incomplete: excludes belowground components;  5-incomplete: excludes breakage into pieces less than dead wood threshold size; 6-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter; 7-foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year).}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{itemize}
\item
  adopt common standards for variables like min diameter of deadwood,
  select soil sampling increments to include a cutoff at 30.
\item
  report 95\% CIs, SE, or STD and n
\item
  report C variables in article text, table, or SI table. EFDB cannot
  accept data digitized from figures
\end{itemize}

>>>>

\clearpage
\begin{figure}
\includegraphics[width=15cm]{figures_tables/C_variable_mapping} \caption{\textbf{Schematic illustrating the carbon pools quantified under IPCC accounting; ForC variables corresponding to the stock, increment, influx and outflux; and relationships among them.} In many cases, the match of ForC variables to IPCC criteria depends upon measurement protocols (e.g., minimum DBH). Additional caveats are as follows: 1- assumes that change in foliage biomass is negligible (see note 7); 2- incomplete: excludes large branch fall; also, under IPCC definitions, outflux from aboveground biomass should include all sizes, influx to deadwood should include only above the minimum diameter chosen for dead wood; 3- incomplete: excludes belowground components;  4-incomplete: excludes breakage into pieces less than dead wood threshold size; 5-incomplete: excludes woody mortality of stems <10 cm DBH, decomposition of dead wood (aboveground and coarse roots) into sizes classified as litter, may exclude branch fall; 6- measurements often limited to decomposition of relatively fine litter and may exclude branches and stems below the dead wood size threshold and/or the more decomposed layers of the O horizon; 7 - foliage production is generally measured by collecting leaf-fall, a method that assumes that the influx = outflux (foliage biomass is roughly constant year-to-year); 8 - excludes branch fall, which is necessary for a full accounting of woody productivity but is typically assumed negligible for calculations of net biomass change.}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{itemize}
\item
  adopt common standards for variables like min diameter of deadwood,
  select soil sampling increments to include a cutoff at 30.
\item
  report 95\% CIs, SE, or STD and n
\item
  report C variables in article text, table, or SI table. EFDB cannot
  accept data digitized from figures
\item
  present calculations of all variables that would be useful to IPCC.
  EFDB requires that data in the database be presented in the original
  article, and as such cannot accept subsequent calculations. For
  example, if aboveground biomass and total biomass are presented, but
  root biomass is not presented, root biomass cannot be subsequently
  calculated and sent to EFDB.
\end{itemize}
